\PassOptionsToPackage{table,xcdraw}{xcolor}

\documentclass[sigconf,review,anonymous]{acmart}
%\acmConference[ESEC/FSE 2021]{The 29th ACM Joint European Software Engineering Conference and Symposium on the Foundations of Software Engineering}{23 - 27 August, 2021}{Athens, Greece}

\acmConference[ICSE 2022]{The 44th International Conference on Software Engineering}{May 21–29, 2022}{Pittsburgh, PA, USA}

%\documentclass[sigconf,review, anonymous]{acmart}
%\documentclass[sigconf]{acmart}

\usepackage{booktabs}   %% For formal tables:
                        %% http://ctan.org/pkg/booktabs
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
                        %% http://ctan.org/pkg/subcaption
\usepackage{array}
\usepackage{amsmath,amsfonts}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
%\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{float} 
\usepackage{listings}
\usepackage{xspace}
\usepackage{multirow}
\usepackage{amsthm}
\newtheorem{definition}{Definition}
\usepackage{balance}

\usepackage[skins]{tcolorbox}

\usepackage{xcolor,pifont}
\newcommand*\colourcheck[1]{%
	\expandafter\newcommand\csname #1check\endcsname{\textcolor{#1}{\ding{52}}}%
}
\colourcheck{blue}
\colourcheck{green}
\colourcheck{red}

\newtcolorbox{myframe}[2][]{%
  enhanced,colback=white,colframe=black,coltitle=black,
  sharp corners,
  toprule=1.0pt,
  rightrule=0.3pt,
  leftrule=0pt,
  bottomrule=0pt,
  fonttitle=\itshape\scshape\large,
  left=0pt,right=5pt,top=5pt,bottom=3pt,
  attach boxed title to top right={yshift=-0.3\baselineskip-0.4pt,xshift=-5mm},
  boxed title style={tile,size=minimal,left=0.2mm,right=0.5mm,
    colback=white,before upper=\strut},
  title=#2,#1
}

%\newcommand{\code}[1]{{\footnotesize\textsf{#1}}}

\newcommand{\tool}{\textsc{CDFix}\xspace}

\newtheorem{Definition}{Definition}
\newtheorem{Claim}{Claim}
\newtheorem{Lemma}{Lemma}
\newtheorem{Theorem}{Theorem}

\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\newtheorem{observation}{Observation}
\newtheorem{property}{Property}
\newcommand{\code}[1]{{\footnotesize\texttt{#1}}}
\usepackage{amsthm}
 \definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}
\lstset{frame=tb,
  language=Java,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=left,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=4
}



\begin{document}

%\title[{\tool}: Deep Fault Localization with Code Coverage Representation Learning]{{\tool}: Deep Fault Localization with Code Coverage Representation Learning}

%\title[Deep Learning-Based Automated Program Repair:\\ Are We There Yet?]{Deep Learning-Based Automated Program Repair:\\ Are We There Yet?}

\title[Context-aware Dual-Task Learning for Automated Program Repair]{Context-aware Dual-Task Learning\\ for Automated Program Repair}

%%%---- AUTHORS BLOCK ------

%Yi Li:New Jersey Institute of Technology;Shaohua Wang:New Jersey
%Institute of Technology;Tien Nguyen:University of Texas at Dallas 

%\author{Yi Li}
%\affiliation{
%\institution{New Jersey Inst. of Technology, USA}
%}
%\email{yl622@njit.edu}
%\author{Shaohua Wang}
%\affiliation{
%\institution{New Jersey Inst. of Technology, USA}
%}
%\email{davidsw@njit.edu}
%\author{Tien N. Nguyen}
%\affiliation{
%\institution{University of Texas at Dallas, USA}
%}
%\email{tien.n.nguyen@utdallas.edu}


%\renewcommand{\shortauthors}{Li, Wang, and Nguyen}

\setcopyright{none}

\settopmatter{printacmref=false, printfolios=false}

\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column


%(1) present information sorted in a way that a CNN can "see" patterns
%discriminating between faulty and non faulty statements more easily;

%(2) identify the actual crash statement to the network;

%(3) present more information to the deep neural network in the form of
%a summary of data dependences for each statement as well as source
%embedding; and

%(4) the suspiciousness of a statement is seen taking into account
%relationships to other statement, as opposed to a statement by itself”



%\input{sections/abstract}
\begin{abstract}
{\bf FIXME.} Automated Program Repair (APR) is very useful in helping
developers in the process of software development and maintenance.
Despite recent advances in deep learning (DL), the DL-based APR
approaches still have limitations in learning bug-fixing code changes
and the context of the surrounding source code of the bug-fixing code
changes.
%which context of the surrounding source code that certain bug-fixing changes should be made. 
These limitations lead to incorrect fixing locations
or fixes. 
In this paper, we introduce {\tool}, a two-tier DL
model that treats APR as code transformation learning from the prior
bug fixes and the surrounding code contexts of the fixes. The
first layer is a tree-based RNN model that learns the contexts
of bug fixes and its result is used as an additional weighting input
for the second layer designed to learn the bug-fixing
code transformations.

We conducted several experiments to evaluate {\tool} in two benchmarks: {\em Defect4J} and {\em Bugs.jar}, and a newly built bug
datasets with a total of +20K real-world bugs in eight projects. We
compared {\tool} against a total of 13 state-of-the-art pattern-based APR
tools. Our results show that {\tool} can auto-fix more bugs than 11 of them, and is
comparable and complementary to the top two pattern-based APR tools in
which there are 7 and 11 unique bugs that they cannot detect,
respectively, but we can. Importantly, {\tool} is fully automated and
data-driven, and does not require hard-coding of bug-fixing patterns
as in those tools. We compared {\tool} against 4 state-of-the-art deep
learning based APR models. {\tool} is able to fix 2.5 times more bugs
than the best performing~baseline.
\end{abstract}


%\settopmatter{printacmref=true, printccs=true, printfolios=false}

%\begin{CCSXML}
%<ccs2012>
%<concept>
%<concept_id>10011007.10011006.10011073</concept_id>
%<concept_desc>Software and its engineering~Software maintenance tools</concept_desc>
%<concept_significance>500</concept_significance>
%</concept>
%</ccs2012>
%\end{CCSXML}

%\ccsdesc[500]{Software and its engineering~Software maintenance tools}

%\keywords{Deep Learning; Automated Program Repair; Context-based Code Transformation Learning}


\maketitle

\input{sections/intro}
\input{sections/motiv}
\input{sections/overview}
\input{sections/approaches_step_1}
\input{sections/approaches_step_2}
\input{sections/approaches_step_3}
\input{sections/experiment}
\input{sections/results}
%\input{sections/key-ideas}

%\section*{Acknowledgments}
%This work was supported in part by the US National Science Foundation
%(NSF) grants CCF-1723215, CCF-1723432, TWC-1723198, CCF-1518897, and
%CNS-1513263.

\newpage

\balance

%\bibliographystyle{plain}
%\bibliographystyle{ACM-Reference-Format}
\bibliographystyle{ACM-Reference-Format}

\bibliography{References}

\end{document}
