\subsection{Threats to Validity}
The threats of this paper come from the following aspects: 
(1) We evaluated our {\tool} on Java and C/C++ code. 
The key modules in {\tool} are language-independent and can be applied to
other types of programming languages. 
(2) We re-implemented CURE as its code was not publicly available online and also the authors of CURE never replied our emails. Under the above circumstances, we tried our best to follow the details in their paper during the implementation. 
(3) The result of our implemented CURE in this paper is lower than the one in its original paper (48 vs 57) on the same Defects4J dataset. The reasons can be two folds: First, in the validation step of the original CURE, the authors first ranked 10,000 candidates and refined the ranking to pick top 5,000 candidates, then validated each candidate. 
In our setting, we set the 5-hr time limit on the validation step, instead of a cut-off on the number of candidates. In the cases that our implemented CURE could not identify a plausible patch after 5-hr limit, on average, we only looped through about ~2350 candidates, which is far fewer than 5,000. Second, we used BigFix as our training dataset, which is different from the one used in the original paper of CURE. However, we evaluated all DL-based approaches using the same training dataset and under the same settings and computing environments. 





%The compared baselines and FixLocator require a dataset with test cases for generating code coverage information, run-time information, and failing traces, thus we only compared them on Defects4J. In the future, we plan to test FixLocator on more types of datasets. 
%(3) The DeepFL is designed for method-level fault localization. To compare it with FixLocator fairly, we use only part of its features that are applicable to statement level fault localization. The other baselines CNNFL and DeepRL4FL can be directly applied on statement-level FL. 
%(4) To compare fairly, we evaluated the baselines using out proposed Hit-N@Set metrics. However, we also tested our FixLocator using the ranking metrics: Hit-N@Top-K. FixLocator is consistently better than all baselines in any metric.